---
title: "Week 6 Discussion"
author: "Alex Parra"
date: "28/6/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tsibble)
library(fpp3)
```

Import 
```{r}
# Data from: https://finance.yahoo.com/quote/SPY/history?period1=728265600&period2=1656374400&interval=1mo&filter=history&frequency=1mo&includeAdjustedClose=true

inputdata <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Week 6/SPY.csv")

# Convert Date column into Date format
inputdata$Date <- yearmonth(inputdata$Date)

# Convert df to tsibble format
inputdata %>%
  as_tsibble(index = Date) -> inputdata 


inputdata
```
```{r}
# Re-index based on trading days
SPY_Shares <- inputdata %>%
  filter(year(Date)>=2015) %>%
  mutate(month = row_number()) #%>%
  #update_tsibble(index = month, regular = TRUE)

SPY_Shares
```




```{r}

SPY_Shares %>%
  autoplot(Adj.Close) +
  labs(y = "Price $US", title = "SPDR S&P 500 ETF Trust Adj. Price",
       subtitle = "(2015 - 2022)")
```


# Simple exponential smoothing model
```{r}
# Estimate parameters
fit <- SPY_Shares %>%
  filter(month <= 76) %>%
  model(ANN = ETS(Adj.Close ~ error("A") + trend("N") + season("N")))

fc <- fit %>%
  forecast(h = 12)

fc %>%
  autoplot(SPY_Shares) +
  geom_line(aes(y = .fitted), col="#D55E00",
            data = augment(fit)) +
  labs(y="Price $US", title="SPDR S&P 500 ETF Trust Adj. Price", subtitle = "Simple exponential smoothing model (2015 - 2022)") +
  guides(colour = "none")



```

cross-validation, evaluate the performance (against the typical metrics) 
```{r}
# Cross validation

# Time series cross-validation accuracy
SPY_Shares_tr <- SPY_Shares %>%
  stretch_tsibble(.init = 60, .step = 1) %>%
  relocate(Date, .id)

SPY_Shares_tr


# Forecast
SPY_Shares_Pred <- SPY_Shares_tr %>%
  model(ANN = ETS(Adj.Close ~ error("A") + trend("N") + season("N"))) %>%
  forecast(h = 12)


# TSCV accuracy
SPY_Shares_Pred %>%
  accuracy(SPY_Shares)
```




# Holt model
```{r}
fit_Holt <- SPY_Shares %>%
  filter(month <= 76) %>%
  model(
    AAN = ETS(Adj.Close ~ error("A") + trend("A") + season("N"))
  )

fc_Holt <- fit_Holt %>% 
  forecast(h = 12)


fc_Holt %>%
  autoplot(SPY_Shares) +
  geom_line(aes(y = .fitted), col="#D55E00",
            data = augment(fit)) +
  labs(y="Price $US", title="SPDR S&P 500 ETF Trust Adj. Price", subtitle = "Holt model (2015 - 2022)") +
  guides(colour = "none")

```

cross-validation, evaluate the performance (against the typical metrics) 
```{r}
# Cross validation

# Forecast
SPY_Shares_Pred_Holt <- SPY_Shares_tr %>%
  model( AAN = ETS(Adj.Close ~ error("A") + trend("A") + season("N"))) %>%
  forecast(h = 12)


# TSCV accuracy
SPY_Shares_Pred_Holt %>%
  accuracy(SPY_Shares)
```




# Holt-Winters model
```{r}
fit_Holt_Winters <- SPY_Shares %>%
  filter(month <= 76) %>%
  model(
    AAA = ETS(Adj.Close ~ error("A") + trend("A") + season("A"))
  )

fc_Holt_Winters <- fit_Holt_Winters %>% 
  forecast(h = 12)


fc_Holt_Winters %>%
  autoplot(SPY_Shares) +
  geom_line(aes(y = .fitted), col="#D55E00",
            data = augment(fit)) +
  labs(y="Price $US", title="SPDR S&P 500 ETF Trust Adj. Price", subtitle = "Holt-Winters model (2015 - 2022)") +
  guides(colour = "none")
```

cross-validation, evaluate the performance (against the typical metrics) 
```{r}
# Cross validation

# Forecast
SPY_Shares_Pred_Holt_Winters <- SPY_Shares_tr %>%
  model( AAA = ETS(Adj.Close ~ error("A") + trend("A") + season("A"))) %>%
  forecast(h = 12)


# TSCV accuracy
SPY_Shares_Pred_Holt_Winters %>%
  accuracy(SPY_Shares)
```


# auto-selected model
```{r}
fit_auto_selected <- SPY_Shares %>%
  filter(month <= 76) %>%
  model(
   auto = ETS(Adj.Close)
  )

fc_auto_selected <- fit_auto_selected %>% 
  forecast(h = 12)


fc_auto_selected %>%
  autoplot(SPY_Shares) +
  geom_line(aes(y = .fitted), col="#D55E00",
            data = augment(fit)) +
  labs(y="Price $US", title="SPDR S&P 500 ETF Trust Adj. Price", subtitle = "auto-selected model ETS(M,A,N) (2015 - 2022)") +
  guides(colour = "none")

report(fit_auto_selected)
```

cross-validation, evaluate the performance (against the typical metrics) 
```{r}
# Cross validation

# Forecast
SPY_Shares_Pred_auto_selected <- SPY_Shares_tr %>%
  model( auto = ETS(Adj.Close)) %>%
  forecast(h = 12)


# TSCV accuracy
SPY_Shares_Pred_auto_selected %>%
  accuracy(SPY_Shares)
```



# Compare
```{r}
# Estimate parameters
fit_compare <- SPY_Shares %>%
  filter(month <= 76) %>%
  model(
    ANN = ETS(Adj.Close ~ error("A") + trend("N") + season("N")),
    AAN = ETS(Adj.Close ~ error("A") + trend("A") + season("N")),
    AAA = ETS(Adj.Close ~ error("A") + trend("A") + season("A")),
    auto = ETS(Adj.Close)
    )

fc_compare <- fit_compare %>%
  forecast(h = 12)

fc_compare %>%
  autoplot(SPY_Shares,level = NULL) +
  #geom_line(aes(y = .fitted), col="#D55E00",
  #          data = augment(fit)) +
  labs(y="Price $US", title="SPDR S&P 500 ETF Trust Adj. Price", subtitle = "(2015 - 2022)") +
  guides(colour = guide_legend(title = "Forecast"))

report(fit_compare)

```


```{r}
# Forecast
SPY_Shares_Pred_compare <- SPY_Shares_tr %>%
  model(
    ANN = ETS(Adj.Close ~ error("A") + trend("N") + season("N")),
    AAN = ETS(Adj.Close ~ error("A") + trend("A") + season("N")),
    AAA = ETS(Adj.Close ~ error("A") + trend("A") + season("A")),
    auto = ETS(Adj.Close)
    ) %>%
  forecast(h = 12)


# TSCV accuracy
SPY_Shares_Pred_compare %>%
  accuracy(SPY_Shares)
```

