---
title: "Final Project"
author: "Alex Parra"
date: "1/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tsibble)
library(fpp3)

```



# Import the datasets


```{r}
hpg_reserve <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/hpg_reserve.csv")
hpg_reserve

hpg_store_info <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/hpg_store_info.csv")
hpg_store_info

air_reserve <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/air_reserve.csv")
air_reserve

air_store_info <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/air_store_info.csv")
air_store_info

air_visit_data <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/air_visit_data.csv")
air_visit_data

store_id_relation <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/store_id_relation.csv")
store_id_relation



date_info <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/date_info.csv")
date_info

sample_submission <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Final Project/Data/recruit-restaurant-visitor-forecasting/sample_submission.csv")
sample_submission
```

# Convert to tsibble

```{r}
################################
#####  sample_submission   #####  
################################
sample_submission_2 = separate(data = sample_submission, col = id, into = c("air", "id", "date"), sep = "_")

sample_submission$air_store_id = paste(sample_submission_2$air,sample_submission_2$id,sep="_")
sample_submission$date = date(sample_submission_2$date)
sample_submission

sample_submission %>%
  as_tsibble(date, key=air_store_id) %>% 
  select(date, air_store_id, id, visitors) -> sample_submission
sample_submission
```



```{r}
########################
#####  date_info   #####  
########################
date_info$date = date(date_info$calendar_date)
date_info %>%
  as_tsibble(index = date ) %>% 
  select(date,day_of_week,holiday_flg)-> date_info
date_info
```

```{r}
################################
#####  store_id_relation   #####  
################################
store_id_relation
```




```{r}
#############################
#####  air_visit_data   #####  
#############################
air_visit_data$date = date(air_visit_data$visit_date)
air_visit_data %>%
  as_tsibble(date, key=air_store_id) %>%
  select(date, air_store_id, visitors)-> air_visit_data
air_visit_data
```

```{r}
#############################
#####  air_store_info   #####  
#############################
air_store_info #This one doesn’t gets converted to tsibble as it doesn’t have a date column

#############################
#####  hpg_store_info   #####  
#############################
hpg_store_info #This one doesn’t gets converted to tsibble as it doesn’t have a date column
```




```{r}
##########################
#####  air_reserve   #####  
##########################
air_reserve$date = date(air_reserve$visit_datetime)
air_reserve$reserve_date = date(air_reserve$reserve_datetime)
air_reserve %>% 
  group_by(air_store_id, date) %>% 
  summarise(reserve_visitors = sum(reserve_visitors)) %>%
  as_tsibble(date, key=air_store_id) %>%
  select(date, air_store_id, reserve_visitors) -> air_reserve
air_reserve
```

```{r}
##########################
#####  hpg_reserve   #####  
##########################
hpg_reserve$date = date(hpg_reserve$visit_datetime)
hpg_reserve$reserve_date = date(hpg_reserve$reserve_datetime)
hpg_reserve %>% 
  group_by(hpg_store_id, date) %>% 
  summarise(reserve_visitors = sum(reserve_visitors)) %>%
  as_tsibble(date, key=hpg_store_id) %>%
  select(date, hpg_store_id, reserve_visitors) -> hpg_reserve
hpg_reserve
```





# Check dimensions

```{r}
########################
#####  date_info   #####  
########################
#date_info
# Number of days
length(unique(date_info$date))
```
```{r}
#############################
#####  air_visit_data   #####  
#############################
#air_visit_data
# Number of diferent stores
length(unique(air_visit_data$air_store_id))
# Number of days
length(unique(air_visit_data$date))
#air_visit_data
```
```{r}
#############################
#####  air_store_info   #####  
#############################
#air_store_info
# Number of diferent stores
length(unique(air_store_info$air_store_id))

```
```{r}
#############################
#####  hpg_store_info   #####  
#############################
#hpg_store_info
# Number of diferent stores
length(unique(hpg_store_info$hpg_store_id))
```
```{r}
##########################
#####  air_reserve   #####  
##########################
#air_reserve
# Number of diferent stores
length(unique(air_reserve$air_store_id))
# Number of days
length(unique(air_reserve$date))
#air_visit_data
```
```{r}
##########################
#####  hpg_reserve   #####  
##########################
#hpg_reserve
# Number of diferent stores
length(unique(hpg_reserve$hpg_store_id))
# Number of days
length(unique(hpg_reserve$date))
#air_visit_data
```

```{r}
################################
#####  sample_submission   #####  
################################
#sample_submission
# Number of diferent stores
length(unique(sample_submission$air_store_id))
# Number of days
length(unique(sample_submission$date))
#air_visit_data
```


# Merge them together

**Create dataset with all the days and stores id combined. There are 821 stores_id and 517 different days. The new dataset needs to have 821 * 517 = 424,457 rows**
```{r}
time_id = fill_gaps(sample_submission, .start = date('2016-01-01')) 
 
time_id %>% 
  left_join(store_id_relation, by = 'air_store_id') %>% # Add the id of the hpg as well
  left_join(date_info, by = 'date') %>% # add the hollidays and day of week
  select(date,day_of_week,holiday_flg, air_store_id, hpg_store_id, id, visitors) ->time_id

#names(time_id)[1] <- 'visitors_Prediction'
names(time_id)[names(time_id) == 'visitors'] <- 'visitors_Pred'

time_id # Number of rows needs to be 424,457
```

**Add the rest of the dataframes**

```{r}
# Add the air_visit_data and air_reserve
time_id %>% 
  left_join(air_visit_data, by = c('date', 'air_store_id')) %>%  
  left_join(air_reserve, by = c('date', 'air_store_id')) -> new_dataset

names(new_dataset)[names(new_dataset) == 'reserve_visitors'] <- 'air_reserve_visitors' # change the name to add the air

# add the hpg_reserve
new_dataset %>% 
  left_join(hpg_reserve, by = c('date', 'hpg_store_id')) ->new_dataset

names(new_dataset)[names(new_dataset) == 'reserve_visitors'] <- 'hpg_reserve_visitors' # change the name to add the air

# add the air_store_info and hpg_store_info
new_dataset %>% 
  left_join(air_store_info, by = 'air_store_id') %>% 
  left_join(hpg_store_info, by = 'hpg_store_id') %>%
  select(date,day_of_week,holiday_flg, air_store_id, hpg_store_id, id, visitors_Pred, visitors, air_reserve_visitors, hpg_reserve_visitors, air_genre_name, hpg_genre_name) -> new_dataset

new_dataset
 

```

**Dataset exploration**
```{r}
# lengths
length(unique(new_dataset$date))
length(unique(new_dataset$day_of_week))
length(unique(new_dataset$holiday_flg))
length(unique(new_dataset$air_store_id))
length(unique(new_dataset$hpg_store_id))
length(unique(new_dataset$id))
length(unique(new_dataset$visitors_Pred))
length(unique(new_dataset$visitors))
length(unique(new_dataset$air_reserve_visitors))
length(unique(new_dataset$hpg_reserve_visitors))
length(unique(new_dataset$air_genre_name))
length(unique(new_dataset$hpg_genre_name))
```

```{r}
# Null count
sum(is.na(new_dataset$date))
sum(is.na(new_dataset$day_of_week))
sum(is.na(new_dataset$holiday_flg))
sum(is.na(new_dataset$air_store_id))
sum(is.na(new_dataset$hpg_store_id))
sum(is.na(new_dataset$id))
sum(is.na(new_dataset$visitors_Pred))
sum(is.na(new_dataset$visitors))
sum(is.na(new_dataset$air_reserve_visitors))
sum(is.na(new_dataset$hpg_reserve_visitors))
sum(is.na(new_dataset$air_genre_name))
sum(is.na(new_dataset$hpg_genre_name))
```

**Create new column with the total reserves. Change the Na to 0 for the reserve columns. Drop the hpg_store_id, visitors_Pred and hpg_genre_name**
```{r}
# change the Na to 0 for the reserve columns
new_dataset[["air_reserve_visitors"]][is.na(new_dataset[["air_reserve_visitors"]])] <- 0
new_dataset[["hpg_reserve_visitors"]][is.na(new_dataset[["hpg_reserve_visitors"]])] <- 0

# Create new column with the total reserve
new_dataset %>%
    rowwise() %>% 
    mutate(total_reserve = sum(c_across(contains("reserve_visitors")), na.rm = T))  %>% 
    ungroup()%>%
    select(date,day_of_week,holiday_flg, air_store_id, id, visitors, air_reserve_visitors, hpg_reserve_visitors, total_reserve, air_genre_name) %>%
  as_tsibble(date, key='air_store_id') ->new_dataset1

new_dataset1
```

**Dataset exploration**
```{r}
new_dataset1 %>%
  filter(date<=date('2017-04-22')) -> train
# lengths
length(unique(train$date))
length(unique(train$day_of_week))
length(unique(train$holiday_flg))
length(unique(train$air_store_id))
length(unique(train$id))
length(unique(train$visitors))
length(unique(train$air_reserve_visitors))
length(unique(train$hpg_reserve_visitors))
length(unique(train$total_reserve))
length(unique(train$air_genre_name))
```

```{r}
# Null count
sum(is.na(train$date))
sum(is.na(train$day_of_week))
sum(is.na(train$holiday_flg))
sum(is.na(train$air_store_id))
sum(is.na(train$id))
sum(is.na(train$visitors))
sum(is.na(train$air_reserve_visitors))
sum(is.na(train$hpg_reserve_visitors))
sum(is.na(train$total_reserve))
sum(is.na(train$air_genre_name))
```


# Need to impute the Visitors values

**First we remove the missing values from the start of the series.**

```{r}
new_dataset1 -> example # create a copy
example$visitors_dup <- example$visitors # duplicate the column
example

example %>% 
  dplyr::group_by(air_store_id) %>% # groupe by the id
  tidyr::fill(visitors_dup, .direction = "down") %>% # impute the duplicated column downwards
  drop_na(visitors_dup) %>% # drop the NA from the duplicated col
  select(date,day_of_week,holiday_flg, air_store_id, id, visitors, visitors_dup, air_reserve_visitors, hpg_reserve_visitors, total_reserve, air_genre_name)  %>% # reorder
  dplyr::ungroup() -> example #ungroup and save
example

example%>% filter(date<=date('2017-04-22'))
```

```{r}
total_na = sum(is.na(example$visitors))
train_na = sum(is.na((example%>% filter(date<=date('2017-04-22')))$visitors))
total_rows = nrow(example)
train_rows = nrow(example%>% filter(date<=date('2017-04-22')))
cat('Number of NA from dataset (2016-01-01 to 2017-05-31):', total_na,'\n')
cat('Number of NA from dataset (2016-01-01 to 2017-04-22):', train_na,'\n')
cat('Number rows from dataset (2016-01-01 to 2017-05-31):', total_rows,'\n')
cat('Number rows from dataset (2016-01-01 to 2017-04-22):', train_rows,'\n')

cat('% Of NA (2016-01-01 to 2017-05-31):', (total_na/total_rows)*100,'%\n')
cat('% Of NA (2016-01-01 to 2017-04-22):', (train_na/train_rows)*100,'%\n')

```
The missing values now is 75,531 from 325,999 rows that means 23.17% if missing values. Just by deleting the initials NA from the time series we have decrease the missing values from 40.99% to 23.17%. This is for the entire dataset, if we look only for the dates between 2016-01-01 to 2017-05-31, we can see that the missing values are 43,512 from 293,980 rows that means: 14.8% of missing values for the dates 2016-01-01 to 2017-04-22.




Now in order to impute the missing values we are going to do it by using the adjacent values. But before doing this imputation, we are going to create a new column indicating which values were NA and which ones weren’t.




```{r}
example %>%
  select(date,day_of_week,holiday_flg, air_store_id, id, visitors, air_reserve_visitors, hpg_reserve_visitors, total_reserve, air_genre_name) %>% # select colmuns
  dplyr::group_by(air_store_id) %>% # group by id
  
  mutate(
    na_val = case_when(visitors!='NA' ~ 0), # new column with 0 on all rows that are not NA
      na_val = replace_na(na_val, 1)) %>% # add to the new column the 1 for the NA in visitors
  mutate(na_val = replace(na_val, !is.na(id), 0)) %>% # Change the 1 to 0 for the dates after 2017-04-22
  mutate(na_val_cumulative = cumsum(na_val)) %>% # columalative column
  tidyr::fill(visitors, .direction = "down") %>% # impute the duplicated column downwards
  dplyr::ungroup() -> final_dataset
final_dataset
```



# Data Visualization
```{r}
final_dataset %>%
  filter(date<= date('2017-04-22')) -> train


```

**Total visitors**
```{r}
train %>%
  mutate(date_copy = date)%>% 
  group_by(date_copy) %>%
  summarise(all_visitors_mean = mean(visitors), all_visitors_sum = sum(visitors)) -> tt

tt%>%
  ggplot(aes(date_copy, all_visitors_sum)) +
  geom_line(col = "Red") +
  labs(title = "Total Visitors", x = "Date", y = "Total visitors")

tt%>%
  ggplot(aes(date_copy, all_visitors_mean)) +
  geom_line(col = "Red") +
  labs(title = "Mean Visitors", x = "Date", y = "Mean visitors")
```
**visitors by restaurant**
```{r}
train %>%
  autoplot(visitors) + 
  theme(legend.position = "none")
```
**Visitors histogram**
```{r}
train %>%
  mutate(date_copy = date)%>% 
  group_by(date_copy) %>%
  summarise(all_visitors_mean = mean(visitors), all_visitors_sum = sum(visitors)) -> tt


par(mfrow=c(2,1))
hist(tt$all_visitors_mean, main = 'Mean Visitors') 
hist(tt$all_visitors_sum, main = 'Total Visitors')
```



**Boxplots of visitors by day**
```{r}
boxplot(visitors~day_of_week, data=train, main="Visitors", xlab="Day of week", ylab="Visitors")


train %>%
  mutate(
    date_copy = date,
    day_of_week_numeric = case_when(
      day_of_week=='Monday' ~1,
      day_of_week=='Tuesday' ~2,
      day_of_week=='Wednesday' ~3,
      day_of_week=='Thursday' ~4,
      day_of_week=='Friday' ~5,
      day_of_week=='Saturday' ~6,
      day_of_week=='Sunday' ~7,
    ))%>% 
  group_by(date_copy) %>%
  summarise(all_visitors_mean = mean(visitors), all_visitors_sum = sum(visitors), day_of_week = mean(day_of_week_numeric) ) -> tt


boxplot(all_visitors_sum~day_of_week, data=tt, main="Total Visitors", xlab="Day of week", ylab="Total Visitors")
boxplot(all_visitors_mean~day_of_week, data=tt, main="Mean Visitors", xlab="Day of week", ylab="Mean Visitors")

```

**Boxplots of visitors by restaurant type**
```{r}
ggplot(train, aes(air_genre_name, visitors)) + geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))  + labs(title = "Visitors", x = "Type of restaurant", y = "Visitors")

train %>%
  mutate(
    date_copy = date,
    air_genre_name_numeric = case_when(
      air_genre_name=='Italian/French' ~1,
      air_genre_name=='Izakaya' ~2,
      air_genre_name=='Dining bar' ~3,
      air_genre_name=='Cafe/Sweets' ~4,
      air_genre_name=='Japanese food' ~5,
      air_genre_name=='Western food' ~6,
      air_genre_name=='Okonomiyaki/Monja/Teppanyaki' ~7,
      air_genre_name=='Yakiniku/Korean food' ~8,
      air_genre_name=='Asian' ~9,
      air_genre_name=='Bar/Cocktail' ~10,
      air_genre_name=='Creative cuisine' ~11,
      air_genre_name=='International cuisine' ~12,
      air_genre_name=='Karaoke/Party' ~13,
      air_genre_name=='Other' ~14,
    )) %>% 
  group_by(air_genre_name) %>%
  summarise(all_visitors_mean = mean(visitors), all_visitors_sum = sum(visitors), air_genre_name_numeric = mean(air_genre_name_numeric) ) %>%
  mutate(
    air_genre_name = case_when(
      air_genre_name_numeric== 1 ~ 'Italian/French',
      air_genre_name_numeric== 2 ~ 'Izakaya',
      air_genre_name_numeric== 3 ~ 'Dining bar',
      air_genre_name_numeric== 4 ~ 'Cafe/Sweets',
      air_genre_name_numeric== 5 ~ 'Japanese food',
      air_genre_name_numeric== 6 ~ 'Western food',
      air_genre_name_numeric== 7 ~ 'Okonomiyaki/Monja/Teppanyaki',
      air_genre_name_numeric== 8 ~ 'Yakiniku/Korean food',
      air_genre_name_numeric== 9 ~ 'Asian',
      air_genre_name_numeric== 10 ~ 'Bar/Cocktail',
      air_genre_name_numeric== 11 ~ 'Creative cuisine',
      air_genre_name_numeric== 12 ~ 'International cuisine',
      air_genre_name_numeric== 13 ~ 'Karaoke/Party',
      air_genre_name_numeric== 14 ~ 'Other',
    ))-> tt

ggplot(tt, aes(air_genre_name, all_visitors_sum)) + geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + labs(title = "Total Visitors", x = "Type of restaurant", y = "Total Visitors")
ggplot(tt, aes(air_genre_name, all_visitors_mean)) + geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + labs(title = "Mean Visitors", x = "Type of restaurant", y = "Mean Visitors")
```







**Reserves by restaurant**
```{r}
train %>%
  autoplot(air_reserve_visitors) + 
  theme(legend.position = "none") + 
  labs(title = "Air Reserves", x = "Date", y = "Reserves")
train %>%
  autoplot(hpg_reserve_visitors) + 
  theme(legend.position = "none") + 
  labs(title = "Hpg Reserves", x = "Date", y = "Reserves")
train %>%
  autoplot(total_reserve) + 
  theme(legend.position = "none") + 
  labs(title = "Air+Hpg Reserves", x = "Date", y = "Reserves")
```

We can see that there are some outliers, lets remove them and impute using the closest points

```{r}
# change outliers to NA
final_dataset %>%
  mutate_at(vars(matches('air_reserve_visitors')), ~ 
                  replace(., air_reserve_visitors >= 450, NA)) -> final_dataset2
# Impute outliers
final_dataset2 %>% 
  dplyr::group_by(air_store_id) %>% # groupe by the id
  tidyr::fill(air_reserve_visitors, .direction = "down") %>% # impute the duplicated column downwards
  dplyr::ungroup() -> final_dataset2 #ungroup and save
# calculate total
final_dataset2 %>% rowwise() %>% 
    mutate(total_reserve = sum(c_across(contains("reserve_visitors")), na.rm = T))  %>% 
    ungroup() %>%
  as_tsibble(date, key='air_store_id') -> final_dataset2

final_dataset2
```




```{r}
final_dataset2 %>%
  filter(date<= date('2017-04-22')) -> train2
train2
```


```{r}
train2 %>%
  autoplot(air_reserve_visitors) + 
  theme(legend.position = "none") + 
  labs(title = "Air Reserves", x = "Date", y = "Reserves")
train2 %>%
  autoplot(hpg_reserve_visitors) + 
  theme(legend.position = "none") + 
  labs(title = "Hpg Reserves", x = "Date", y = "Reserves")
train2 %>%
  autoplot(total_reserve) + 
  theme(legend.position = "none") + 
  labs(title = "Air+Hpg Reserves", x = "Date", y = "Reserves")
```

```{r}
train2 %>%
  mutate(date_copy = date)%>% 
  group_by(date_copy) %>%
  summarise(total_reserve_mean = mean(total_reserve), total_reserve_sum = sum(total_reserve)) -> tt

tt%>%
  ggplot(aes(date_copy, total_reserve_sum)) +
  geom_line(col = "Red") +
  labs(title = "Total Reserves", x = "Date", y = "Total Reserves")

tt%>%
  ggplot(aes(date_copy, total_reserve_mean)) +
  geom_line(col = "Red") +
  labs(title = "Mean Reserves", x = "Date", y = "Mean Reserves")
```

```{r}
train2 %>%
  mutate(date_copy = date)%>% 
  group_by(date_copy) %>%
  summarise(total_reserve_mean = mean(total_reserve), total_reserve_sum = sum(total_reserve)) -> tt


par(mfrow=c(2,1))
hist(tt$total_reserve_mean, main = 'Mean Reserves') 
hist(tt$total_reserve_sum, main = 'Total Reserves')
```


```{r}

train2 %>% 
  mutate(date_copy = date)%>% 
  group_by(date_copy) %>%
  summarise(holiday_flg = mean(holiday_flg), total_visitors_mean = mean(visitors))%>%
  mutate(
    holiday_flg_text = case_when(
      holiday_flg==0 ~ 'No holiday',
      holiday_flg==1 ~ 'holiday')) %>%
  ungroup() -> tt
tt
ggplot(tt, aes(holiday_flg_text, total_visitors_mean)) + geom_boxplot() +
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))  + 
  labs(title = "Mean Visitors", x = "Holiday type", y = "Mean Visitors")
```


```{r}
library(ResourceSelection)
train2 %>% 
  mutate(
    air_genre_name = case_when(
      air_genre_name=='Italian/French' ~1,
      air_genre_name=='Izakaya' ~2,
      air_genre_name=='Dining bar' ~3,
      air_genre_name=='Cafe/Sweets' ~4,
      air_genre_name=='Japanese food' ~5,
      air_genre_name=='Western food' ~6,
      air_genre_name=='Okonomiyaki/Monja/Teppanyaki' ~7,
      air_genre_name=='Yakiniku/Korean food' ~8,
      air_genre_name=='Asian' ~9,
      air_genre_name=='Bar/Cocktail' ~10,
      air_genre_name=='Creative cuisine' ~11,
      air_genre_name=='International cuisine' ~12,
      air_genre_name=='Karaoke/Party' ~13,
      air_genre_name=='Other' ~14
      ),
    day_of_week = case_when(
      day_of_week=='Monday' ~1,
      day_of_week=='Tuesday' ~2,
      day_of_week=='Wednesday' ~3,
      day_of_week=='Thursday' ~4,
      day_of_week=='Friday' ~5,
      day_of_week=='Saturday' ~6,
      day_of_week=='Sunday' ~7,
    )) %>%
  as_tibble(date) %>%
  select(date, 
         day_of_week, 
         holiday_flg,
         visitors,
         air_reserve_visitors,
         hpg_reserve_visitors,
         total_reserve,
         air_genre_name,
         na_val,
         na_val_cumulative) ->tt
tt


#kdepairs(tt)
tt %>%
  GGally::ggpairs() + labs(title = "Variables Relations")
```
```{r}
kdepairs(tt)
```


```{r}
train2
```

















































################################################################################
################################################################################
################################################################################
################################################################################
################################################################################
################################################################################
################################################################################
################################################################################
################################################################################
################################################################################
################################################################################












## Convert the datasets to tsibble
```{r}
air_reserve$date = date(air_reserve$visit_datetime)
air_reserve$reserve_date = date(air_reserve$reserve_datetime)
air_reserve %>% 
  group_by(air_store_id, date) %>% 
  summarise(reserve_visitors = sum(reserve_visitors)) %>%
  as_tsibble(date, key=air_store_id) %>%
  select(date, air_store_id, reserve_visitors) -> air_reserve
air_reserve

air_reserve %>%
  as_tibble(date, key='air_store_id') %>%
  complete(date, air_store_id) %>%
  arrange(air_store_id) -> air_reserve
air_reserve

# Number of diferent stores
length(unique(air_reserve$air_store_id))
# Number of days
length(unique(air_reserve$date))
```

```{r}

air_visit_data$date = date(air_visit_data$visit_date)
air_visit_data %>%
  as_tsibble(date, key=air_store_id) %>%
  select(date, air_store_id, visitors)-> air_visit_data
air_visit_data

air_visit_data %>%
  complete(date, air_store_id) %>%
  arrange(air_store_id) -> air_visit_data
air_visit_data

# Number of diferent stores
length(unique(air_visit_data$air_store_id))
# Number of days
length(unique(air_visit_data$date))
```



```{r}
date_info$date = date(date_info$calendar_date)
date_info %>%
  as_tsibble(index = date ) %>% 
  select(date,day_of_week,holiday_flg)-> date_info
date_info

# Number of days
length(unique(date_info$date))
```







## Merge then together

```{r}
# Number of diferent stores
length(unique(air_store_info$air_store_id))

# Number of days
length(unique(air_visit_data$date))
```



```{r}
#Merge Air_reserve and air_store_info using the air_store_id as key
#air_reserve_P_store_info = dplyr::inner_join(air_reserve, air_store_info, by=c('air_store_id'))
air_visit_data_P_reserve = merge(x=air_visit_data ,y=air_reserve, by.x=c('date','air_store_id'),by.y = c('date','air_store_id'), all= T)
air_visit_data_P_reserve
length(unique(air_visit_data_P_reserve$air_store_id))# size needs to be 829


#Merge air_visit_data_P_reserve and air_store_info using the date and air_store_id as key
#air_reserve_P_store_info_P_visit_data = dplyr::inner_join(air_visit_data_P_reserve, air_store_info, by=c('date','air_store_id'))
air_visit_data_P_reserve_P_store_info = merge(x=air_visit_data_P_reserve,y=air_store_info, by.x='air_store_id',by.y = 'air_store_id',all= T)
air_visit_data_P_reserve_P_store_info
length(unique(air_visit_data_P_reserve_P_store_info$air_store_id))# size needs to be 829


#air_visit_data_P_reserve_P_store_info %>%
#  complete(date, air_store_id) ->air_visit_data_P_reserve_P_store_info



air_data = merge(x=date_info,y=air_visit_data_P_reserve_P_store_info, by.x="date",by.y = "date",all= T)
air_data
```
```{r}
sum(is.na(air_reserve_P_store_info$air_genre_name))

sum(is.na(air_reserve_P_store_info_P_visit_data$air_genre_name))

sum(is.na(air_reserve_P_store_info_P_visit_data$air_genre_name))
```
```{r}
air_store_info %>%
  filter(air_store_id == 'air_0241aa3964b7f861')
```








```{r}
air_data %>%
  as_tsibble(date, key=air_store_id) %>%
  select(date, day_of_week, air_store_id, air_genre_name, holiday_flg, reserve_visitors, visitors)
  
```


```{r}
length(unique(air_data$air_store_id))

length(unique(air_reserve$air_store_id))

length(unique(air_store_info$air_store_id))

length(unique(air_visit_data$air_store_id))
```
```{r}
air_reserve

air_store_info

air_visit_data

date_info
```



```{r}
# Merge
#air_reserve <- merge(air_reserve, air_store_info[, c("air_store_id", "air_genre_name")], by="air_store_id")
# Convert to tsibble and order columns
#air_reserve %>% as_tsibble(visit_datetime, key='air_store_id') %>% select(visit_datetime, air_store_id, #reserve_visitors, air_genre_name) -> air_reserve
#air_reserve
```











```{r}

```

