---
title: "Midterm Project"
author: "Alex Parra"
date: "22/6/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tsibble)
library(fpp3)
library(ResourceSelection)
```


# Import the datasets

First the train dataset
```{r}
# Data from: https://www.kaggle.com/c/covid19-global-forecasting-week-5/data?select=submission.csv

train <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Midterm Project/Data/train.csv")

# Convert Date column into Date format
train$Date <- date(train$Date)

#Split by target
#ConfirmedCases <- inputdata[inputdata$Target=='ConfirmedCases',]
#Fatalities <- inputdata[inputdata$Target=='Fatalities',]

# Remouved target column
#ConfirmedCases <- select(ConfirmedCases, -Target)
#Fatalities <- select(Fatalities, -Target)

# change name of TargetValue column
#colnames(ConfirmedCases)[which(names(ConfirmedCases) == "TargetValue")] <- "ConfirmedCases"
#colnames(Fatalities)[which(names(Fatalities) == "TargetValue")] <- "Fatalities"

# Join together the values as two different columns.
#ConfirmedCases$Fatalities <- c(Fatalities$Fatalities)


# Convert df to tsibble format
train %>%
  as_tsibble(index = Date, key = c(County, Province_State, Country_Region, Target)) -> train

train


```


Second the test dataset
```{r}
# Data from: https://www.kaggle.com/c/covid19-global-forecasting-week-5/data?select=submission.csv

test <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Midterm Project/Data/test.csv")

# Convert Date column into Date format
test$Date <- date(test$Date)

# Convert df to tsibble format
test %>%
  as_tsibble(index = Date, key = c(County, Province_State, Country_Region, Target)) -> test

test
```

And the submission dataset

```{r}
# Data from: https://www.kaggle.com/c/covid19-global-forecasting-week-5/data?select=submission.csv

submission <- read.csv("D:/Personal/Alex/Uni/MS IA/2 Curso/Summer 2022/Predictive Models/Assignments/Midterm Project/Data/submission.csv")

submission
```






# Explore the data

## Country Names:
```{r}
#train 
# get the names of countries, provinces and counties
country_names = unique(train$Country_Region)
print('---------------------------------------------------------------------------------------------------')
print('country_names')
print('---------------------------------------------------------------------------------------------------')
print(country_names)

```

## Province Names:

```{r}
province_names = unique(train$Province_State)
print('---------------------------------------------------------------------------------------------------')
print('province_names')
print('---------------------------------------------------------------------------------------------------')
province_names

```

## counties Names:

```{r}
county_names = unique(train$County)
print('---------------------------------------------------------------------------------------------------')
print('county_names')
print('---------------------------------------------------------------------------------------------------')
county_names
```

## Provinces by country:

We can see that only 8 countries have subdivisions in this dataset. 
The country with the largest number of provinces is the US with 54, this is because it counts District of Columbia, Guam, Puerto Rico and the Virgin Islands.

The second country with the most provinces in China with 33, followed by Canada with 12, France and the UK with 10, Australia with 8, the Netherlands with 4 and Denmark with 2

```{r}
countries_with_subdivisions = unique(duplicates(train %>% filter (Target == 'ConfirmedCases'), key = Country_Region, Date)$Country_Region)

print('countries_with_subdivisions: ')

countries_with_subdivisions
print('---------------------------------------------------------------------------------------------------')
for (country in countries_with_subdivisions) {
  
  # get only that country
  province= train %>% filter (Country_Region == country)
  
  count = length(unique(province$Province_State)) -1
  
  # print country name + number of province
  print(paste(country, ' (', count, ')' ))
  
  # print proviences names
  print(unique(province$Province_State))
  print('---------------------------------------------------------------------------------------------------')
}
```



## Counties by province:
Here we can see the complete list of all the provinces with their respective counties. In this case all the provinces belong to the US and we see that in this case Guam, Puerto Rico and the Virgin Islands do not have subdivisions
```{r}
provinces_with_subdivisions = unique(duplicates(train %>% filter (Target == 'ConfirmedCases'), key = Province_State, Date)$Province_State)

print( paste('provinces_with_subdivisions: (', length(provinces_with_subdivisions)-1 ,')'))

provinces_with_subdivisions
print('---------------------------------------------------------------------------------------------------')
for (province in provinces_with_subdivisions[-1]) {
  
  # get only that province
  county= train %>% filter (Province_State == province)
  
  count = length(unique(county$County)) -1
  
  # print province name + number of province
  print(paste(province, ' (', count, ')' ))
  
  # print proviences names
  print(unique(county$County))
  print('---------------------------------------------------------------------------------------------------')
}
```





## Plot some countries
```{r}
#train
train %>% 
  filter(Country_Region == 'US'| Country_Region == 'Canada'| Country_Region == 'Italy'| Country_Region == 'Germany') %>%
  filter(Province_State== '') %>%
  select(Date, Target, Country_Region, TargetValue) -> data #, Province_State

# list of countries explored
country_list = c('US', 'Canada', 'Italy', 'Germany')

# Graphs
autoplot(data %>% 
  filter(Country_Region == 'US'))

autoplot(data %>% 
  filter(Country_Region == 'Canada'))

autoplot(data %>% 
  filter(Country_Region == 'Italy'))

autoplot(data %>% 
  filter(Country_Region == 'Germany'))

# Boxplot 
boxplot(TargetValue~Target, data=data %>% filter(Country_Region == 'US'), main="US",
   xlab="Target", ylab="TargetValue")#Country_Region

boxplot(TargetValue~Target, data=data %>% filter(Country_Region == 'Canada'), main="Canada",
   xlab="Target", ylab="TargetValue")#Country_Region

boxplot(TargetValue~Target, data=data %>% filter(Country_Region == 'Italy'), main="Italy",
   xlab="Target", ylab="TargetValue")#Country_Region

boxplot(TargetValue~Target, data=data %>% filter(Country_Region == 'Germany'), main="Germany",
   xlab="Target", ylab="TargetValue")#Country_Region

# Histograms
for (cc in country_list) {
  data %>% filter(Country_Region == cc) -> dd
  
  dd %>% filter(Target == "ConfirmedCases") -> confirmed_Cases 
  dd %>% filter(Target == "Fatalities") -> fatalities 
  
  par(mfrow=c(2,1))
  hist(confirmed_Cases$TargetValue, main = paste0(cc,' confirmed_Cases')) 
  hist(fatalities$TargetValue, main = paste0(cc,' fatalities'))
}
```

```{r}
# Filter
train %>% 
  filter(Country_Region == 'US'| Country_Region == 'Canada'| Country_Region == 'Italy'| Country_Region == 'Germany') %>%
  filter(Province_State== '')  %>%
  mutate(Target = case_when(
    Target=='ConfirmedCases' ~ 0,
    Target=='Fatalities' ~ 1)) %>%
  as_tsibble(index = Date, key = Weight ) %>% 
  select(Date, Population, Weight, Target, TargetValue) -> data_US_Canada_Italy_Germany

data_US_Canada_Italy_Germany

kdepairs(data_US_Canada_Italy_Germany)


train %>%
  filter(Province_State== '')%>% 
  mutate(Target = case_when(
    Target=='ConfirmedCases' ~ 0,
    Target=='Fatalities' ~ 1)) %>%
  as_tsibble(index = Date, key = Weight ) %>% 
  select(Date, Population, Weight, Target, TargetValue) -> data_whole_world

data_whole_world

kdepairs(data_whole_world)


train %>%
  filter(County== '')%>% 
  mutate(Target = case_when(
    Target=='ConfirmedCases' ~ 0,
    Target=='Fatalities' ~ 1)) %>%
  #as_tsibble(index = Date, key = Weight ) %>% 
  select(Date, Population, Weight, Target, TargetValue) -> data_whole_world_with_provinces

data_whole_world_with_provinces[,1:5]

kdepairs(data_whole_world_with_provinces[,1:5])
```



```{r}
data_US_Canada_Italy_Germany %>%
  GGally::ggpairs() + labs(title = "US Canada Italy and Germany")

data_whole_world %>%
  GGally::ggpairs() + labs(title = "Whole World")

data_whole_world_with_provinces %>%
  GGally::ggpairs(columns = 1:5) + labs(title = "Whole World with provinces")
```




# Models

## Basic models
using only original information, without any outside datasets

### US, Canada, Italy, Germany
only for those 4 countries
```{r}
train %>% 
  filter(Country_Region == 'US'| Country_Region == 'Canada'| Country_Region == 'Italy'| Country_Region == 'Germany') %>%
  
  filter(Province_State== '')  %>%
  
  mutate_at(.vars = 'TargetValue', .funs = list(~ ifelse(TargetValue < 0, 0, .))) %>% # Convert negative values to 0
  
  mutate(Target_num = case_when(
    Target=='ConfirmedCases' ~ 0,
    Target=='Fatalities' ~ 1),
    TargetValue_cumulative = cumsum(TargetValue), # Get a column of cumulative values
    PandemicStart = case_when(
    TargetValue_cumulative!=0 ~ 1,
    TargetValue_cumulative==0 ~ 0)# Column indicating the start of the pandemic
    ) %>%
  
  select(Date, County, Province_State, Country_Region, Population, Weight, Target, Target_num, PandemicStart, TargetValue_cumulative, TargetValue) -> data_train

#data_train$TargetValue <- as.integer(data_train$TargetValue)
data_train$TargetValue <- as.double(data_train$TargetValue)
#as.double()

data_train
```

```{r}
data_train %>% 
  select(Date, Population, Weight, Target_num, PandemicStart,TargetValue_cumulative, TargetValue) %>%
  GGally::ggpairs(columns = 1:7)
```

Build models:

  TargetValue ~ Trend + season
  TargetValue ~ Trend + season + Weight

  TargetValue ~ lag(TargetValue)
  TargetValue ~ Trend + lag(TargetValue)
  TargetValue ~ Season + lag(TargetValue)
  TargetValue ~ Trend + season + lag(TargetValue)

  TargetValue ~ Trend + season + PandemicStart
  TargetValue ~ Trend + season + PandemicStart + lag(TargetValue)

  log(TargetValue) ~ Trend + season + lag(log(TargetValue))
  log(TargetValue) ~ Trend + season + PandemicStart + lag(log(TargetValue))
  
```{r}
# get around 80% to train, rest 20% to validate
data_train %>% 
  filter( Date <'2020-05-14' ) -> data_train_split80

#data_train_split80 %>% filter(TargetValue<=0)

fit_model <- data_train_split80 %>%
  model(
        ts = TSLM(TargetValue ~ trend() + season()),
        
        tsw = TSLM(TargetValue ~ trend() + season() + Weight),
        
        l1 = TSLM(TargetValue ~ lag(TargetValue, n=1)),
        l2 = TSLM(TargetValue ~ lag(TargetValue, n=2)),
        l4 = TSLM(TargetValue ~ lag(TargetValue, n=4)),
        l6 = TSLM(TargetValue ~ lag(TargetValue, n=6)),
        l8 = TSLM(TargetValue ~ lag(TargetValue, n=8)),
        
        tl1 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=1)),
        tl2 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=2)),
        tl4 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=4)),
        tl6 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=6)),
        tl8 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=8)),
        
        sl1 = TSLM(TargetValue ~ season() + lag(TargetValue, n=1)),
        sl2 = TSLM(TargetValue ~ season() + lag(TargetValue, n=2)),
        sl4 = TSLM(TargetValue ~ season() + lag(TargetValue, n=4)),
        sl6 = TSLM(TargetValue ~ season() + lag(TargetValue, n=6)),
        sl8 = TSLM(TargetValue ~ season() + lag(TargetValue, n=8)),
        
        tsl1 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=1)),
        tsl2 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=2)),
        tsl4 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=4)),
        tsl6 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=6)),
        tsl8 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=8)),
        
        tsS = TSLM(TargetValue ~ trend() + season() + PandemicStart),
        
        tsSl1 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=1)),
        tsSl2 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=2)),
        tsSl4 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=4)),
        tsSl6 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=6)),
        tsSl8 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=8)),
        
        log_tsl1 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=1)),
        log_tsl2 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=2)),
        log_tsl4 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=4)),
        log_tsl6 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=6)),
        
        log_tsSl1 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=1)),
        log_tsSl2 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=2)),
        log_tsSl4 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=4)),
        log_tsSl6 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=6))
        
        ) 

fit_model



# Make forecast
forecast(fit_model, data_train) -> data_Pred
data_Pred
```



```{r}
# TSCV accuracy
data_Pred %>%
  accuracy(data_train) %>%
  group_by(.model,Target) %>%   summarize(
    avg_ME = mean(ME),
    avg_RMSE = mean(RMSE),
    avg_MAE = mean(MAE),
    avg_ACF1 = mean(ACF1),
    avg_MPE = mean(MPE),
    avg_MAPE = mean(MAPE),
    avg_MASE = mean(MASE),
    avg_RMSSE = mean(RMSSE)
    ) %>%
  arrange(avg_RMSE) -> accuracy_US_Canada_Italy_Germany
accuracy_US_Canada_Italy_Germany

data_Pred %>%
  accuracy(data_train) %>%
  group_by(.model) %>%   summarize(
    avg_ACF1 = mean(ACF1),
    ) %>%
  arrange(avg_ACF1)

glance(fit_model) %>%
  group_by(.model,Target) %>% 
  summarize(
    avg_adj_r_squared = mean(adj_r_squared),
    avg_CV = mean(CV),
    avg_AIC = mean(AIC),
    avg_AICc = mean(AICc),
    avg_BIC = mean(BIC),
    ) %>%
  arrange(desc(avg_adj_r_squared)) -> glance_US_Canada_Italy_Germany
glance_US_Canada_Italy_Germany
  
```


```{r}
data_Pred %>%
  filter(Country_Region == 'US' & Target == 'ConfirmedCases') %>%
  filter(.model == "l1" | .model == "sl1" | .model == "tl1" | .model == "tsl1" | .model == "log_tsl1") %>%
  autoplot(data_train_US,level = NULL, colour = 'red') +
  labs(y = "Cases",
       title = "Confirmed Cases for USA",
       subtitle = "(2020/01/23 - 2020/06/10)") +
  guides(colour = guide_legend(title = "Forecast"))

data_Pred %>%
  filter(Country_Region == 'US' & Target == 'Fatalities') %>%
  filter(.model == "l1" | .model == "sl1" | .model == "tl1" | .model == "tsl1" | .model == "log_tsl1") %>%
  autoplot(data_train_US,level = NULL, colour = 'red') +
  labs(y = "Cases",
       title = "Fatalities for USA",
       subtitle = "(2020/01/23 - 2020/06/10)") +
  guides(colour = guide_legend(title = "Forecast"))
```



### All countries
Only for the countries
Now lets run the previous models on the hole globe, and see the results, not only on 4 countries (In this case, ignoring the provinces and counties, only countries)

```{r}
train %>% 
  filter(Province_State== '')  %>%
  
  mutate_at(.vars = 'TargetValue', .funs = list(~ ifelse(TargetValue < 0, 0, .))) %>% # Convert negative values to 0
  
  mutate(Target_num = case_when(
    Target=='ConfirmedCases' ~ 0,
    Target=='Fatalities' ~ 1),
    TargetValue_cumulative = cumsum(TargetValue), # Get a column of cumulative values
    PandemicStart = case_when(
    TargetValue_cumulative!=0 ~ 1,
    TargetValue_cumulative==0 ~ 0)# Column indicating the start of the pandemic
    ) %>%
  
  select(Date, County, Province_State, Country_Region, Population, Weight, Target, Target_num, PandemicStart, TargetValue_cumulative, TargetValue) -> data_train_whole_glove

#data_train$TargetValue <- as.integer(data_train$TargetValue)
data_train_whole_glove$TargetValue <- as.double(data_train_whole_glove$TargetValue)
#as.double()

data_train_whole_glove

# Get correlations
data_train_whole_glove %>% 
  select(Date, Population, Weight, Target_num, PandemicStart,TargetValue_cumulative, TargetValue) %>%
  GGally::ggpairs(columns = 1:7)
```


```{r}
# get around 80% to train, rest 20% to validate
data_train_whole_glove %>% 
  filter( Date <'2020-05-14' ) -> data_train_whole_glove_split80



fit_model_whole_glove <- data_train_whole_glove_split80 %>%
  model(
        ts = TSLM(TargetValue ~ trend() + season()),
        
        tsw = TSLM(TargetValue ~ trend() + season() + Weight),
        
        l1 = TSLM(TargetValue ~ lag(TargetValue, n=1)),
        l2 = TSLM(TargetValue ~ lag(TargetValue, n=2)),
        l4 = TSLM(TargetValue ~ lag(TargetValue, n=4)),
        l6 = TSLM(TargetValue ~ lag(TargetValue, n=6)),
        l8 = TSLM(TargetValue ~ lag(TargetValue, n=8)),
        
        tl1 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=1)),
        tl2 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=2)),
        tl4 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=4)),
        tl6 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=6)),
        tl8 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=8)),
        
        sl1 = TSLM(TargetValue ~ season() + lag(TargetValue, n=1)),
        sl2 = TSLM(TargetValue ~ season() + lag(TargetValue, n=2)),
        sl4 = TSLM(TargetValue ~ season() + lag(TargetValue, n=4)),
        sl6 = TSLM(TargetValue ~ season() + lag(TargetValue, n=6)),
        sl8 = TSLM(TargetValue ~ season() + lag(TargetValue, n=8)),
        
        tsl1 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=1)),
        tsl2 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=2)),
        tsl4 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=4)),
        tsl6 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=6)),
        tsl8 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=8)),
        
        tsS = TSLM(TargetValue ~ trend() + season() + PandemicStart),
        
        tsSl1 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=1)),
        tsSl2 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=2)),
        tsSl4 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=4)),
        tsSl6 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=6)),
        tsSl8 = TSLM(TargetValue ~ trend() + season() + PandemicStart + lag(TargetValue, n=8)),
        
        log_tsl1 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=1)),
        log_tsl2 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=2)),
        log_tsl4 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=4)),
        log_tsl6 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=6)),
        
        log_tsSl1 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=1)),
        log_tsSl2 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=2)),
        log_tsSl4 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=4)),
        log_tsSl6 = TSLM(log1p(TargetValue) ~ trend() + season() + PandemicStart + lag(log1p(TargetValue), n=6))
        
        ) 

fit_model_whole_glove



# Make forecast
forecast(fit_model_whole_glove, data_train_whole_glove) -> data_Pred_whole_glove
data_Pred_whole_glove
```

```{r}
# TSCV accuracy
data_Pred_whole_glove %>%
  accuracy(data_train_whole_glove) %>%
  group_by(.model,Target) %>%   summarize(
    avg_ME = mean(ME),
    avg_RMSE = mean(RMSE),
    avg_MAE = mean(MAE),
    avg_ACF1 = mean(ACF1),
    avg_MPE = mean(MPE),
    avg_MAPE = mean(MAPE),
    avg_MASE = mean(MASE),
    avg_RMSSE = mean(RMSSE)
    ) %>%
  arrange(avg_RMSE) -> accuracy_whole_glove
accuracy_whole_glove

data_Pred_whole_glove %>%
  accuracy(data_train_whole_glove) %>%
  group_by(.model) %>%   summarize(
    avg_ACF1 = mean(ACF1),
    ) %>%
  arrange(avg_ACF1)

glance(fit_model_whole_glove) %>%
  group_by(.model,Target) %>% 
  summarize(
    avg_adj_r_squared = mean(adj_r_squared),
    avg_CV = mean(CV),
    avg_AIC = mean(AIC),
    avg_AICc = mean(AICc),
    avg_BIC = mean(BIC),
    ) %>%
  arrange(desc(avg_adj_r_squared)) -> glance_whole_glove
glance_whole_glove
  
```






### All Dataset
Only for the countries
Now lets run the previous models on the hole globe, and see the results (In this case, including the provinces and counties), in this case we only run a couple of models and not all, this is done in order to increase excetution time:
```{r}
train %>% 
  mutate_at(.vars = 'TargetValue', .funs = list(~ ifelse(TargetValue < 0, 0, .))) %>% # Convert negative values to 0
  
  mutate(Target_num = case_when(
    Target=='ConfirmedCases' ~ 0,
    Target=='Fatalities' ~ 1),
    TargetValue_cumulative = cumsum(TargetValue), # Get a column of cumulative values
    PandemicStart = case_when(
    TargetValue_cumulative!=0 ~ 1,
    TargetValue_cumulative==0 ~ 0)# Column indicating the start of the pandemic
    ) %>%
  
  select(Date, County, Province_State, Country_Region, Population, Weight, Target, Target_num, PandemicStart, TargetValue_cumulative, TargetValue) -> data_train_whole_glove_with_provincies_counties

#data_train$TargetValue <- as.integer(data_train$TargetValue)
data_train_whole_glove_with_provincies_counties$TargetValue <- as.double(data_train_whole_glove_with_provincies_counties$TargetValue)
#as.double()

#data_train_whole_glove_with_provincies_counties

```



```{r}
# get around 80% to train, rest 20% to validate
data_train_whole_glove_with_provincies_counties %>% 
  filter( Date <'2020-05-14' ) -> data_train_whole_glove_with_provincies_counties_split80



fit_model_whole_glove_with_provincies_counties <- data_train_whole_glove_with_provincies_counties_split80 %>%
  model(
        #tl1 = TSLM(TargetValue ~ trend() + lag(TargetValue, n=1)),
        
        #sl1 = TSLM(TargetValue ~ season() + lag(TargetValue, n=1)),
        
        tsl1 = TSLM(TargetValue ~ trend() + season() + lag(TargetValue, n=1)),
        
        #log_tsl1 = TSLM(log1p(TargetValue) ~ trend() + season() + lag(log1p(TargetValue), n=1))
        ) 

fit_model_whole_glove_with_provincies_counties



# Make forecast
forecast(fit_model_whole_glove_with_provincies_counties, data_train_whole_glove_with_provincies_counties) -> data_Pred_whole_glove_with_provincies_counties
#data_Pred_whole_glove_with_provincies_counties
```

```{r}
# TSCV accuracy
data_Pred_whole_glove_with_provincies_counties %>%
  accuracy(data_train_whole_glove_with_provincies_counties) %>%
  group_by(.model,Target) %>%   summarize(
    avg_ME = mean(ME),
    avg_RMSE = mean(RMSE),
    avg_MAE = mean(MAE),
    avg_ACF1 = mean(ACF1),
    avg_MPE = mean(MPE),
    avg_MAPE = mean(MAPE),
    avg_MASE = mean(MASE),
    avg_RMSSE = mean(RMSSE)
    ) %>%
  arrange(avg_RMSE) -> accuracy_whole_glove_with_provincies_counties
accuracy_whole_glove_with_provincies_counties

data_Pred_whole_glove_with_provincies_counties %>%
  accuracy(data_train_whole_glove_with_provincies_counties) %>%
  group_by(.model) %>%   summarize(
    avg_ACF1 = mean(ACF1),
    ) %>%
  arrange(avg_ACF1)

glance(fit_model_whole_glove_with_provincies_counties) %>%
  group_by(.model,Target) %>% 
  summarize(
    avg_adj_r_squared = mean(adj_r_squared),
    avg_CV = mean(CV),
    avg_AIC = mean(AIC),
    avg_AICc = mean(AICc),
    avg_BIC = mean(BIC),
    ) %>%
  arrange(desc(avg_adj_r_squared)) -> glance_whole_glove_with_provincies_counties
glance_whole_glove_with_provincies_counties
```




